---
title: "Clutter, rain and waves"
author: "M. Bradaric"
date: "1/26/2021"
output:
  html_document:
    code_folding: "hide"
    number_sections: false
    keep_md: true
    fig_width: 6 
    fig_height: 4
---
<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 8px;
}
h1.title {
  font-size: 38px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 22px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>
---


```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.height='110%',out.width = '110%'}
library(lubridate)
library(dplyr)
library(ggplot2)
library(plotly)
library(imputeTS)

seaH <- read.csv("C:/Users/mbradar/Documents/Sea_waves/sea_2019_2020_L_hourly.csv",sep=";")
vert <- read.csv("C:/Users/mbradar/Documents/Robin/data/Birds/Luchterduinen/allseasons_2019-2020_vert.csv",sep=";")
vertH <- read.csv("C:/Users/mbradar/Documents/Robin/data/Birds/Luchterduinen/allseasons_2019-2020_hourly_vert.csv",sep=";")
clutH <- read.csv("C:/Users/mbradar/Documents/Robin/data/Clutter/Luchterduinen/clutter_2019-2020_horiz_hourly.csv",sep=";")
clutV <- read.csv("C:/Users/mbradar/Documents/Robin/data/Clutter/Luchterduinen/clutter_2019-2020_vert_hourly.csv",sep=";")
rainH <- read.csv("C:/Users/mbradar/Documents/Rain-Johannes/rain_2019-2020_L_hourly.csv", sep=";")
```


## Birds and clutter
##### This is a timeseries of bird counts from vertical radar(upper plot) and clutter extracted from 
##### horizontal radar (middle) and vertical radar (bottom)
##### Use slider to zoom in and out 



```{r,message=FALSE,echo=FALSE,warning=FALSE,fig.height=10, out.width='110%'}
birds <- ggplot(vert, aes(timestamph)) +
  geom_bar(mapping = aes(x = timestamph, y = ..count..,colour=vert$classification, fill=vert$classification), stat = "count",show.legend = T) +
  scale_fill_manual(values = c("magenta","red","orange","yellow"), name="", drop=F)+
  scale_colour_manual(values  = c("magenta","red","orange","yellow"), name="", drop=F)+
  theme_bw()+
  theme(axis.title.y = element_text(size=12), legend.text=element_text(size=9), 
        legend.title=element_text(size=12, face="bold"), legend.position = "bottom",
        panel.grid = element_blank(),
        axis.text.y=element_text(size=10), axis.text.x=element_text(angle=90), plot.margin = unit(c(0,0,0,0), "cm"),
        axis.title.x = element_blank(), plot.title = element_text(size = 18, face = "bold"))+
  scale_x_datetime(date_breaks="days", date_labels="%Y-%m-%d",
                   limits=c(as.POSIXct("2019-02-15 17:00:00"), as.POSIXct("2020-12-01 07:00:00")))+
  scale_y_continuous(name = "Counts")

fig1 <- ggplotly(birds,dynamicTicks = T)
fig2 <- plot_ly(clutH) 
fig2 <- fig2 %>% add_lines(data=clutH, name="land_H", x = ~timestamph, y = ~l_mask*100,
                        line = list(color="green",width=0.5),showlegend=TRUE)
fig2 <- fig2 %>% add_lines(data=clutH, name="variable_H", x = ~timestamph, y = ~v_mask*100,
                         line = list(color="brown",width=0.5),showlegend=TRUE)
fig2 <- fig2 %>% add_lines(data=clutH, name="rain_H", x = ~timestamph, y = ~r_mask*100,
                         line = list(color="blue",width=0.5),showlegend=TRUE)

fig3 <- plot_ly(clutV) 
fig3 <- fig3 %>% add_lines(data=clutV, name="land_V", x = ~timestamph, y = ~l_mask*100,
                        line = list(color="forestgreen",width=0.5),showlegend=TRUE)
fig3 <- fig3 %>% add_lines(data=clutV, name="variable_V", x = ~timestamph, y = ~v_mask*100,
                         line = list(color="chocolate",width=0.5),showlegend=TRUE)
fig3 <- fig3 %>% add_lines(data=clutV, name="rain_V", x = ~timestamph, y = ~r_mask*100,
                         line = list(color="darkslateblue",width=0.5),showlegend=TRUE)

fig <-  subplot(fig1, fig2,fig3, nrows = 3, shareX = TRUE) 
fig %>% rangeslider(start=as.POSIXct("2019-02-15 17:00:00"),end=as.POSIXct("2019-06-01 17:00:00"), borderwidth = 0.2) %>%
   layout(yaxis=list(title="Count", tickfont = list(size=8), titlefont=list(size=14,face="bold")),   yaxis2=list(title="Percentage",range=c(0,100), tickfont = list(size=8), titlefont=list(size=14,face="bold")), yaxis3=list(title="Percentage",range=c(0,100), tickfont = list(size=8), titlefont=list(size=14,face="bold")), titleX = TRUE, titleY = TRUE) 
```
## Following graphs show comparison of clutter (land, rain and variant) between two radar beams

## Land clutter comparison
```{r,,message=FALSE,echo=FALSE,warning=FALSE,out.width='110%'}

clut1 <- ggplot() +
  geom_line(data=clutH, aes(timestamph,l_mask*100,colour="horizontal"))+
  geom_line(data=clutV,aes(timestamph,l_mask*100,colour="vertical"))+
  scale_colour_manual(name="Radar",values=c("green","forestgreen"))+
  theme_bw()+
  theme(axis.title.y = element_text(size=12), legend.text=element_text(size=9), 
        legend.title=element_text(size=12, face="bold"), legend.position = "bottom",
        panel.grid = element_blank(),
        axis.text.y=element_text(size=9), axis.text.x=element_text(angle=90), plot.margin = unit(c(0,0,0,0), "cm"),
        axis.title.x = element_blank(), plot.title = element_text(size = 18, face = "bold"))+
 scale_x_datetime(date_breaks="days", date_labels="%Y-%m-%d",
                   limits=c(as.POSIXct("2019-02-15 17:00:00"), as.POSIXct("2020-12-01 07:00:00")))+
  scale_y_continuous(name = "Clutter %")

ggplotly(clut1, dynamicTicks = T) %>%
  rangeslider(start=as.POSIXct("2019-02-15 17:00:00"),end=as.POSIXct("2019-06-01 17:00:00"), borderwidth = 1) %>%
  layout(hovermode = "x")
```



## Rain clutter comparison
```{r,message=FALSE,echo=FALSE,warning=FALSE,out.width='110%'}
clut2 <- ggplot(clutH, aes(timestamph,r_mask*10,colour="horizontal")) +
  geom_line()+
  geom_line(data=clutV,aes(timestamph,r_mask*10,colour="vertical"))+
  scale_colour_manual(name="Radar",values=c("blue","darkslateblue"))+
  theme_bw()+
  theme(axis.title.y = element_text(size=12), legend.text=element_text(size=9), 
        legend.title=element_text(size=12, face="bold"), legend.position = "bottom",
        panel.grid = element_blank(),
        axis.text.y=element_text(size=9), axis.text.x=element_text(angle=90), plot.margin = unit(c(0,0,0,0), "cm"),
        axis.title.x = element_blank(), plot.title = element_text(size = 18, face = "bold"))+
 scale_x_datetime(date_breaks="days", date_labels="%Y-%m-%d",
                   limits=c(as.POSIXct("2019-02-15 17:00:00"), as.POSIXct("2020-12-01 07:00:00")))+
  scale_y_continuous(name = "Clutter %")

ggplotly(clut2, dynamicTicks = T) %>%
  rangeslider(borderwidth = 1) %>%
  layout(hovermode = "x")
```


## Variant clutter comparison
```{r,message=FALSE,echo=FALSE,warning=FALSE,out.width='110%'}

clut3 <- ggplot(clutH, aes(timestamph,v_mask*100,colour="horizontal")) +
  geom_line()+
  geom_line(data=clutV,aes(timestamph,v_mask*100,colour="vertical"))+
  scale_colour_manual(name="Radar",values=c("brown","chocolate"))+
  theme_bw()+
  theme(axis.title.y = element_text(size=12), legend.text=element_text(size=9), 
        legend.title=element_text(size=12, face="bold"), legend.position = "bottom",
        panel.grid = element_blank(),
        axis.text.y=element_text(size=9), axis.text.x=element_text(angle=90), plot.margin = unit(c(0,0,0,0), "cm"),
        axis.title.x = element_blank(), plot.title = element_text(size = 18, face = "bold"))+
 scale_x_datetime(date_breaks="days", date_labels="%Y-%m-%d",
                   limits=c(as.POSIXct("2019-02-15 17:00:00"), as.POSIXct("2020-12-01 07:00:00")))+
  scale_y_continuous(name = "Clutter (%)")
 

ggplotly(clut3, dynamicTicks = T) %>%
  rangeslider(borderwidth = 1) %>%
  layout(hovermode = "x") 
```


## Rain clutter filter from both radars and rain data from KNMI

#### note that the KNMI rain data doesn't come from the exact location of Luchterduninen, but from a point
#### that is more than 10 km away and closer to the coast
#### the graph below shows (top down): bird counts (vertical radar), rain data from KNMI, rain clutter 
#### activity in the horizontal radar and rain clutter activity in the vertical radar

```{r,message=FALSE,echo=FALSE,warning=FALSE,fig.height=10,out.width='110%'}
rainy <- ggplot(rainH,aes(timestamph,mean,colour="mean")) +
  geom_line() +
  scale_colour_manual(values = c("royalblue4"), name=" ")+
  theme_bw()+
  theme(axis.title.y = element_text(size=12), legend.text=element_text(size=9), 
        legend.title=element_text(size=12, face="bold"), legend.position = "bottom",
        panel.grid = element_blank(),
        axis.text.y=element_text(size=9), axis.text.x=element_text(angle=90), plot.margin = unit(c(0,0,0,0), "cm"),
        axis.title.x = element_blank(), plot.title = element_text(size = 18, face = "bold"))+
 scale_x_datetime(date_breaks="days", date_labels="%Y-%m-%d",
                   limits=c(as.POSIXct("2019-02-15 17:00:00"), as.POSIXct("2020-12-01 07:00:00")))+
  scale_y_continuous(name = "Rain (mm)")
rain1 <- ggplotly(rainy,dynamicTicks = TRUE)

rain2 <- plot_ly(clutH) 
rain2 <- rain2 %>% add_lines(data=clutH, name="rain_H", x = ~timestamph, y = ~r_mask*100,
                         line = list(color="blue",width=0.5),showlegend=TRUE)
rain3 <- plot_ly(clutV) 
rain3 <- rain3 %>% add_lines(data=clutV, name="rain_V", x = ~timestamph, y = ~r_mask*100,
                         line = list(color="darkslateblue",width=0.5),showlegend=TRUE)

rainfig <-  subplot(fig1,rain1,rain2,rain3,nrows = 4, shareX = TRUE) 
rainfig %>% rangeslider(start=as.POSIXct("2019-02-15 17:00:00"),end=as.POSIXct("2019-06-01 17:00:00"), borderwidth = 0.2) %>%
   layout(yaxis=list(title="Count", tickfont = list(size=8), titlefont=list(size=14,face="bold")),          
          yaxis2=list(title="Rain (mm)",range=c(0,100), tickfont = list(size=8), titlefont=list(size=14,face="bold")),
          yaxis3=list(title="Percentage",range=c(0,100), tickfont = list(size=8), titlefont=list(size=14,face="bold")),
          yaxis4=list(title="Percentage",range=c(0,100), tickfont = list(size=8), titlefont=list(size=14,face="bold")),
            titleX = TRUE, titleY = TRUE) 


```


## Variant clutter filter from both radars and rain data from KNMI

#### same as the graph above, just with the variant filter from different radar beams 

```{r,message=FALSE,echo=FALSE,warning=FALSE,fig.height=10,out.width='110%'}
rain5 <- plot_ly(clutH) 
rain5 <- rain5 %>% add_lines(data=clutH, name="variant_H", x = ~timestamph, y = ~r_mask*100,
                         line = list(color="brown"),showlegend=TRUE)
rain6 <- plot_ly(clutV) 
rain6 <- rain6 %>% add_lines(data=clutV, name="variant_V", x = ~timestamph, y = ~r_mask*100,
                         line = list(color="chocolate"),showlegend=TRUE)

rainfig <-  subplot(fig1,rain1,rain5,rain6, nrows = 4, shareX = TRUE) 
rainfig %>% rangeslider(start=as.POSIXct("2019-02-15 17:00:00"),end=as.POSIXct("2019-06-01 17:00:00"), borderwidth = 0.2) %>%
   layout(yaxis=list(title="Count", tickfont = list(size=8), titlefont=list(size=14,face="bold")),          
          yaxis2=list(title="Rain (mm)",range=c(0,100), tickfont = list(size=8), titlefont=list(size=14,face="bold")),
          yaxis3=list(title="Percentage",range=c(0,100), tickfont = list(size=8), titlefont=list(size=14,face="bold")),
          yaxis4=list(title="Percentage",range=c(0,100), tickfont = list(size=8), titlefont=list(size=14,face="bold")),
            titleX = TRUE, titleY = TRUE) 
```


## Sea wave data from waterinfo

#### the sea wave data comes from a station close to Luchterduinen called IJgeul 1 boei
#### data of the nearby stations is not consistent: some of them have data for only 2019 (which is the case
#### with the one presented here), while some of them have data for only last three months of 2020

#### the subplots shown below are in the following order (top down): bird counts (vertical radar), sea wave
#### data, rain data from KNMI, rain clutter activity in the horizontal radar and rain clutter activity in
#### the vertical radar
```{r,message=FALSE,echo=FALSE,warning=FALSE,fig.height=10,out.width='110%'}
seas <- ggplot(seaH,aes(timestamph,height,colour="height")) +
  geom_line() +
  scale_colour_manual(values = c("aquamarine4"), name=" ")+
  theme_bw()+
  theme(axis.title.y = element_text(size=12), legend.text=element_text(size=9), 
        legend.title=element_text(size=12, face="bold"), legend.position = "bottom",
        panel.grid = element_blank(),
        axis.text.y=element_text(size=9), axis.text.x=element_text(angle=90), plot.margin = unit(c(0,0,0,0), "cm"),
        axis.title.x = element_blank(), plot.title = element_text(size = 18, face = "bold"))+
 scale_x_datetime(date_breaks="days", date_labels="%Y-%m-%d",
                   limits=c(as.POSIXct("2019-02-15 17:00:00"), as.POSIXct("2019-12-01 07:00:00")))+
  scale_y_continuous(name = "Sea waves (cm)")
sea1 <- ggplotly(seas,dynamicTicks = TRUE)

rainfig <-  subplot(fig1,sea1,rain1,rain2,rain3, nrows = 5, shareX = TRUE) 
rainfig %>% rangeslider(start=as.POSIXct("2019-02-15 17:00:00"),end=as.POSIXct("2019-06-01 17:00:00"), borderwidth = 0.2) %>%
   layout(yaxis=list(title="Count", tickfont = list(size=8), titlefont=list(size=14,face="bold")),                yaxis2=list(title="Sea waves (cm)",range=c(0,100), tickfont = list(size=8),             titlefont=list(size=14,face="bold")), 
          yaxis3=list(title="Rain (mm)",range=c(0,100), tickfont = list(size=8), titlefont=list(size=14,face="bold")),
          yaxis4=list(title="Percentage",range=c(0,100), tickfont = list(size=8), titlefont=list(size=14,face="bold")),
          yaxis6=list(title="Percentage",range=c(0,100), tickfont = list(size=8), titlefont=list(size=14,face="bold")),
          yaxis7=list(title="Percentage",range=c(0,100), tickfont = list(size=8), titlefont=list(size=14,face="bold")),
            titleX = TRUE, titleY = TRUE) 

```


## Sea wave data from waterinfo 

#### same as the graph above, just with the variant clutter activity from both radar beams

```{r,message=FALSE,echo=FALSE,warning=FALSE,fig.height=10,out.width='110%'}
rainfig <-  subplot(fig1,sea1,rain5,rain6, nrows = 4, shareX = TRUE) 
rainfig %>% rangeslider(start=as.POSIXct("2019-02-15 17:00:00"),end=as.POSIXct("2019-06-01 17:00:00"), borderwidth = 0.2) %>%
   layout(yaxis=list(title="Count", tickfont = list(size=8), titlefont=list(size=14,face="bold")),                yaxis2=list(title="Height (cm)",range=c(0,100), tickfont = list(size=8),             titlefont=list(size=14,face="bold")), 
          yaxis3=list(title="Percentage",range=c(0,100), tickfont = list(size=8), titlefont=list(size=14,face="bold")),
          yaxis4=list(title="Percentage",range=c(0,100), tickfont = list(size=8), titlefont=list(size=14,face="bold")),
            titleX = TRUE, titleY = TRUE, rangeslider = list(type = "date", thickness=0.1)) 
```

