---
title: "Spearman correlations"
author: "M. Bradaric"
date: "1/8/2021"
output:
  html_document:
    code_folding: "hide"
    number_sections: false
    keep_md: true
    fig_width: 6 
    fig_height: 4
---
<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 8px;
}
h1.title {
  font-size: 38px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 22px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>

## Env. variables on count
### 2019
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE}
require(gridExtra)
library(ggpubr)
library(dplyr)
birds1 <- read.csv("C:/Users/mbradar/Documents/Robin/data/spring_2019_br.csv",sep=";")
weather1 <- read.csv("C:/Users/mbradar/Documents/Robin/data/spring_2019_wr.csv",sep=";")
birds2 <- read.csv("C:/Users/mbradar/Documents/Robin/data/autumn_2019_br.csv",sep=";")
weather2 <- read.csv("C:/Users/mbradar/Documents/Robin/data/autumn_2019_wr.csv",sep=";")
rownames(weather1) <- NULL
rownames(weather2) <- NULL

joinedS <- left_join(birds1,weather1,by=c("time","altitude_layer"))
my_dataS <-  joinedS %>%
  group_by(altitude_layer)%>%
  summarise(count=sum(count,na.rm = T), wind_ass=mean(wind_ass),temp=mean(temp),rh=mean(r),
            crwc=mean(crwc),cc=mean(cc))

joinedA <- left_join(birds2,weather2,by=c("time","altitude_layer"))
my_dataA <-  joinedA %>%
  group_by(altitude_layer)%>%
  summarise(count=sum(count,na.rm = T), wind_ass=mean(wind_ass),temp=mean(temp),rh=mean(r),
            crwc=mean(crwc),cc=mean(cc))
```

#### wind_assistance

```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}
windS <- ggscatter(my_dataS, x = "wind_ass", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "wind_ass", ylab = "count")
windA <- ggscatter(my_dataA, x = "wind_ass", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "wind_ass", ylab = "count")
grid.arrange(windS, windA, ncol=2)
```

#### temp 
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}
tempS <- ggscatter(my_dataS, x = "temp", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "temp", ylab = "count")

tempA <- ggscatter(my_dataA, x = "temp", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "temp", ylab = "count")
grid.arrange(tempS, tempA, ncol=2)
```

#### cc
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}
ccS <- ggscatter(my_dataS, x = "cc", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "cc", ylab = "count")
ccA <- ggscatter(my_dataA, x = "cc", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "cc", ylab = "count")
grid.arrange(ccS, ccA, ncol=2)
```

#### crwc
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}
crwcS <- ggscatter(my_dataS, x = "crwc", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "crwc", ylab = "count")
crwcA <- ggscatter(my_dataA, x = "crwc", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "crwc", ylab = "count")
grid.arrange(crwcS, crwcA, ncol=2)
```

#### rh
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}

rhS <- ggscatter(my_dataS, x = "rh", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "rh", ylab = "count")
rhA <- ggscatter(my_dataA, x = "rh", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "rh", ylab = "count")
grid.arrange(rhS, rhA, ncol=2)

```
### 2020

```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE}
require(gridExtra)
library(ggpubr)
library(dplyr)
birds3 <- read.csv("C:/Users/mbradar/Documents/Robin/data/spring_2020_br.csv",sep=";")
weather3 <- read.csv("C:/Users/mbradar/Documents/Robin/data/spring_2020_wr.csv",sep=";")
birds4 <- read.csv("C:/Users/mbradar/Documents/Robin/data/autumn_2020_br.csv",sep=";")
weather4 <- read.csv("C:/Users/mbradar/Documents/Robin/data/autumn_2020_wr.csv",sep=";")
rownames(weather3) <- NULL
rownames(weather4) <- NULL

joinedS1 <- left_join(birds3,weather3,by=c("time","altitude_layer"))
my_dataS1 <-  joinedS1 %>%
  group_by(altitude_layer)%>%
  summarise(count=sum(count,na.rm = T), wind_ass=mean(wind_ass),temp=mean(temp),rh=mean(r),
            crwc=mean(crwc),cc=mean(cc))

joinedA1 <- left_join(birds4,weather4,by=c("time","altitude_layer"))
my_dataA1 <-  joinedA1 %>%
  group_by(altitude_layer)%>%
  summarise(count=sum(count,na.rm = T), wind_ass=mean(wind_ass),temp=mean(temp),rh=mean(r),
            crwc=mean(crwc),cc=mean(cc))
```

#### wind_assistance

```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}
windS1 <- ggscatter(my_dataS1, x = "wind_ass", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "wind_ass", ylab = "count")
windA1 <- ggscatter(my_dataA1, x = "wind_ass", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "wind_ass", ylab = "count")
grid.arrange(windS1, windA1, ncol=2)
```

#### temp 
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}
tempS1 <- ggscatter(my_dataS1, x = "temp", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "temp", ylab = "count")

tempA1 <- ggscatter(my_dataA1, x = "temp", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "temp", ylab = "count")
grid.arrange(tempS1, tempA1, ncol=2)
```

#### cc
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}
ccS1 <- ggscatter(my_dataS1, x = "cc", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "cc", ylab = "count")
ccA1 <- ggscatter(my_dataA1, x = "cc", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "cc", ylab = "count")
grid.arrange(ccS1, ccA1, ncol=2)
```

#### crwc
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}
crwcS1 <- ggscatter(my_dataS1, x = "crwc", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "crwc", ylab = "count")
crwcA1 <- ggscatter(my_dataA1, x = "crwc", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "crwc", ylab = "count")
grid.arrange(crwcS1, crwcA1, ncol=2)
```

#### rh
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}

rhS1 <- ggscatter(my_dataS1, x = "rh", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "rh", ylab = "count")
rhA1 <- ggscatter(my_dataA1, x = "rh", y = "count", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "rh", ylab = "count")
grid.arrange(rhS1, rhA1, ncol=2)

```

## Altitude of min/max env. variable on altitude of count
### 2019
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE}
my_dataSa <- joinedS %>%
  group_by(night.x,altitude_layer) %>%
  summarise(count=sum(count,na.rm = T), wind_ass=mean(wind_ass),temp=mean(temp),rh=mean(r),
            crwc=mean(crwc),cc=mean(cc))

my_dataAa <- joinedA %>%
  group_by(night.x,altitude_layer) %>%
  summarise(count=sum(count,na.rm = T), wind_ass=mean(wind_ass),temp=mean(temp),rh=mean(r),
            crwc=mean(crwc),cc=mean(cc))

alt_countS <- my_dataSa %>%
  group_by(night.x) %>%
  slice(which.max(count))

alt_countA <- my_dataAa %>%
  group_by(night.x) %>%
  slice(which.max(count))

alt_tempS <- my_dataSa %>%
  group_by(night.x) %>%
  slice(which.max(temp))

alt_tempA <- my_dataAa %>%
  group_by(night.x) %>%
  slice(which.max(temp))

alt_windS <- my_dataSa %>%
  group_by(night.x) %>%
  slice(which.max(wind_ass))

alt_windA <- my_dataAa %>%
  group_by(night.x) %>%
  slice(which.max(wind_ass))

alt_rhS <- my_dataSa %>%
  group_by(night.x) %>%
  slice(which.min(rh))

alt_rhA <- my_dataAa %>%
  group_by(night.x) %>%
  slice(which.min(rh))

alt_ccS <- my_dataSa %>%
  group_by(night.x) %>%
  slice(which.min(cc))

alt_ccA <- my_dataAa %>%
  group_by(night.x) %>%
  slice(which.min(cc))

alt_crwcS <- my_dataSa %>%
  group_by(night.x) %>%
  slice(which.min(crwc))

alt_crwcA <- my_dataAa %>%
  group_by(night.x) %>%
  slice(which.min(crwc))

my_dataSaa <- Reduce(function(...) merge(..., by="night.x",all.x=TRUE), list(alt_countS, alt_tempS, alt_windS,alt_crwcS,alt_rhS,alt_ccS))
my_dataSaaa <- my_dataSaa[,c(1:2,9,16,23,30,37)]
colnames(my_dataSaaa)[colnames(my_dataSaaa)==c("night.x","altitude_layer.x","altitude_layer.y","altitude_layer.x.1", "altitude_layer.y.1","altitude_layer.x.2","altitude_layer.y.2")] <- c("night","alt_cnt","alt_t","alt_w","alt_cw","alt_rh","alt_cc")

my_dataAaa <- Reduce(function(...) merge(..., by="night.x",all.x=TRUE), list(alt_countA, alt_tempA, alt_windA,alt_crwcA,alt_rhA,alt_ccA))
my_dataAaaa <- my_dataAaa[,c(1:2,9,16,23,30,37)]
colnames(my_dataAaaa)[colnames(my_dataAaaa)==c("night.x","altitude_layer.x","altitude_layer.y","altitude_layer.x.1", "altitude_layer.y.1","altitude_layer.x.2","altitude_layer.y.2")] <- c("night","alt_cnt","alt_t","alt_w","alt_cw","alt_rh","alt_cc")

```

#### wind
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}
windSa <- ggscatter(my_dataSaaa, x = "alt_w", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_w", ylab = "alt_count")

windAa <- ggscatter(my_dataAaaa, x = "alt_w", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_w", ylab = "alt_count")

grid.arrange(windSa, windAa, ncol=2)

```

#### temp
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}

tempSa <- ggscatter(my_dataSaaa, x = "alt_t", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_t", ylab = "alt_count")

tempAa <- ggscatter(my_dataAaaa, x = "alt_t", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_t", ylab = "alt_count")

grid.arrange(tempSa, tempAa, ncol=2)

```

#### cc
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}
ccSa <- ggscatter(my_dataSaaa, x = "alt_cc", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_cc", ylab = "alt_count")
ccAa <- ggscatter(my_dataAaaa, x = "alt_cc", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_cc", ylab = "alt_count")
grid.arrange(ccSa, ccAa, ncol=2)
```

#### rh
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}
rhSa <- ggscatter(my_dataSaaa, x = "alt_rh", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_rh", ylab = "alt_count")
rhAa <- ggscatter(my_dataAaaa, x = "alt_rh", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_rh", ylab = "alt_count")
grid.arrange(rhSa, rhAa, ncol=2)
```

#### crwc
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}
crwcSa <- ggscatter(my_dataSaaa, x = "alt_cw", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_cw", ylab = "alt_count")
crwcAa <- ggscatter(my_dataAaaa, x = "alt_cw", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_cw", ylab = "alt_count")
```


### 2020
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE}
my_dataSa1 <- joinedS1 %>%
  group_by(night.x,altitude_layer) %>%
  summarise(count=sum(count,na.rm = T), wind_ass=mean(wind_ass),temp=mean(temp),rh=mean(r),
            crwc=mean(crwc),cc=mean(cc))

my_dataAa1 <- joinedA1 %>%
  group_by(night.x,altitude_layer) %>%
  summarise(count=sum(count,na.rm = T), wind_ass=mean(wind_ass),temp=mean(temp),rh=mean(r),
            crwc=mean(crwc),cc=mean(cc))

alt_countS1 <- my_dataSa1 %>%
  group_by(night.x) %>%
  slice(which.max(count))

alt_countA1 <- my_dataAa1 %>%
  group_by(night.x) %>%
  slice(which.max(count))

alt_tempS1 <- my_dataSa1 %>%
  group_by(night.x) %>%
  slice(which.max(temp))

alt_tempA1 <- my_dataAa1 %>%
  group_by(night.x) %>%
  slice(which.max(temp))

alt_windS1 <- my_dataSa1 %>%
  group_by(night.x) %>%
  slice(which.max(wind_ass))

alt_windA1 <- my_dataAa1 %>%
  group_by(night.x) %>%
  slice(which.max(wind_ass))

alt_rhS1 <- my_dataSa1 %>%
  group_by(night.x) %>%
  slice(which.min(rh))

alt_rhA1 <- my_dataAa1 %>%
  group_by(night.x) %>%
  slice(which.min(rh))

alt_ccS1 <- my_dataSa1 %>%
  group_by(night.x) %>%
  slice(which.min(cc))

alt_ccA1 <- my_dataAa1 %>%
  group_by(night.x) %>%
  slice(which.min(cc))

alt_crwcS1 <- my_dataSa1 %>%
  group_by(night.x) %>%
  slice(which.min(crwc))

alt_crwcA1 <- my_dataAa1 %>%
  group_by(night.x) %>%
  slice(which.min(crwc))

my_dataSaa1 <- Reduce(function(...) merge(..., by="night.x",all.x=TRUE), list(alt_countS1, alt_tempS1, alt_windS1,alt_crwcS1,alt_rhS1,alt_ccS1))
my_dataSaaa1 <- my_dataSaa1[,c(1:2,9,16,23,30,37)]
colnames(my_dataSaaa1)[colnames(my_dataSaaa1)==c("night.x","altitude_layer.x","altitude_layer.y","altitude_layer.x.1", "altitude_layer.y.1","altitude_layer.x.2","altitude_layer.y.2")] <- c("night","alt_cnt","alt_t","alt_w","alt_cw","alt_rh","alt_cc")

my_dataAaa1 <- Reduce(function(...) merge(..., by="night.x",all.x=TRUE), list(alt_countA1, alt_tempA1, alt_windA1,alt_crwcA1,alt_rhA1,alt_ccA1))
my_dataAaaa1 <- my_dataAaa1[,c(1:2,9,16,23,30,37)]
colnames(my_dataAaaa1)[colnames(my_dataAaaa1)==c("night.x","altitude_layer.x","altitude_layer.y","altitude_layer.x.1", "altitude_layer.y.1","altitude_layer.x.2","altitude_layer.y.2")] <- c("night","alt_cnt","alt_t","alt_w","alt_cw","alt_rh","alt_cc")

```

#### wind
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}
windSa1 <- ggscatter(my_dataSaaa1, x = "alt_w", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_w", ylab = "alt_count")

windAa1 <- ggscatter(my_dataAaaa1, x = "alt_w", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_w", ylab = "alt_count")

grid.arrange(windSa1, windAa1, ncol=2)

```

#### temp
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}

tempSa1 <- ggscatter(my_dataSaaa1, x = "alt_t", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_t", ylab = "alt_count")

tempAa1 <- ggscatter(my_dataAaaa1, x = "alt_t", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_t", ylab = "alt_count")

grid.arrange(tempSa1, tempAa1, ncol=2)

```

#### cc
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}
ccSa1 <- ggscatter(my_dataSaaa1, x = "alt_cc", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_cc", ylab = "alt_count")
ccAa1 <- ggscatter(my_dataAaaa1, x = "alt_cc", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_cc", ylab = "alt_count")
grid.arrange(ccSa1, ccAa1, ncol=2)
```

#### rh
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}
rhSa1 <- ggscatter(my_dataSaaa1, x = "alt_rh", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_rh", ylab = "alt_count")
rhAa1 <- ggscatter(my_dataAaaa1, x = "alt_rh", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_rh", ylab = "alt_count")
grid.arrange(rhSa1, rhAa1, ncol=2)
```

#### crwc
```{r,results='hide',message=FALSE,echo=FALSE,warning=FALSE,out.width = '110%'}
crwcSa1 <- ggscatter(my_dataSaaa1, x = "alt_cw", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_cw", ylab = "alt_count")
crwcAa1 <- ggscatter(my_dataAaaa1, x = "alt_cw", y = "alt_cnt", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "spearman",
          xlab = "alt_cw", ylab = "alt_count")
```
